Empirical normative theories

### 2020-07-16 simple.tex
Typo proof
Rm old commands
Simplified and sorted commands

The symbol $¬$ is a negation operator on $\allprops$, such that $\forall \prop \in \allprops: ¬¬\prop = \prop$. This article also uses this symbol as a negation operator on $\Phi$, defined as follows, $\forall \prop \in \allprops$: $¬\propposs = (¬\prop, \mathit{sure})$ and $¬\propsure = (¬\prop, \mathit{poss})$. Observe that $¬¬\phi = \phi$. (The symbol $¬$ is also used in this article to negate classical mathematical propositions; this should create no confusion.)
As usual with binary relations, $\hist \nileadsto[i] \phi$ means $(\hist, \phi) \notin {\ileadsto[i]}$.

@@

To lighten notations, $\ileadstoi$ and $\ileadstosti$ will generally be denoted by $\ileadsto$ and $\ileadstosts$, these symbols being understood as the result of a function of $i$. 
When the symbol $\ileadsto$ or $\ileadstosts$ is used in a formula without $i$ being bound, the binding $\forall i \in I$ is implied.

@@

	To prove the theorem, build a finite sequence of arguments in $\gargs[i, \phi]$, starting with any $\ar_0 \in \ileadstoinv(\phi)$. Observe that $\ar_0 \in \gargs[i, \phi]$. Given $k \in 2\N$, if $\ar_k \nileadstosti \phi$, define $\ar_{k + 2}$ using the deduction following the last lemma, obtaining $\ar_{k + 2} \in \gargs[i, \phi] \cap \dfp^\frac{k + 2}{2}(\ar_0)$. 
	By definition of an empirical theory, $\exists k \in \N \suchthat \dfp^k(\ar_0) = \emptyset$, thus, this process ends with some $\ar$ such that $\ar \ileadstosti \phi$.
\end{proof}

\subsection{Effectively comparing models}
Model: for a given $i$. Defends $\prop$. $\exists \ar_1 \in \args_\eta \suchthat \ar_1 \ileadstoe \prop$. Then, $\forall \ar_2 \in \gargs \suchthat (\ar_2, \ar_1) \ileadstoe ¬\prop: \exists \ar_3 \in \args_\eta \suchthat (\ar_3, \ar_2) \ileadstoe \prop.$

\section{Decision situation}
\newcommand{\alltopic}{T^*}

@@

\subsection{Example model}
\begin{itemize}
	\item $\ar_0 = \text{“Veg bec of ethics and health”}$
	\item $\ar_1 = \text{“Ethics is not defined”}$
	\item $\ar_2 = \text{“It is since Aristotle at least”}$
	\item $\ar_1' = \text{“Health isn’t important”}$
	\item $\ar_2' = \text{“Ask my grandmother”}$
	\item $\ar_1 \mbeats \ar_0$, $\ar_1' \mbeats \ar_0$
	\item $\ar_2 \mbeats \ar_1$, $\ar_2' \mbeats \ar_1'$
	\item $\ar_0 + \ar_2 \mbeats \ar_1$
	\item $\ar_1' \mbeats \ar_0 + \ar_2$
	\item $\ar_0 + \ar_2' \mbeats \ar_1'$
	\item $\ar_1 \mbeats \ar_0 + \ar_2'$
	\item $\ar_0 + \ar_2 + \ar_2' \mbeats \ar_1$
	\item $\ar_0 + \ar_2 + \ar_2' \mbeats \ar_1'$
\end{itemize}

>>>>

The symbol $¬$ is a negation operator on $\allprops$, such that $\forall \prop \in \allprops: ¬¬\prop = \prop$. This article also uses this symbol as a negation operator on $\Phi$, defined as follows, $\forall \prop \in \allprops$: $¬\propposs = (¬\prop, \mathit{sure})$ and $¬\propsure = (¬\prop, \mathit{poss})$. Observe that $¬¬\phi = \phi$. (The symbol $¬$ is also used in this article to negate classical mathematical propositions; this should create no confusion.)
As usual with binary relations, $\hist \nileadstoi \phi$ means $(\hist, \phi) \notin {\ileadstoi}$.

@@

@@

	To prove the theorem, build a finite sequence of arguments in $\gargs[i, \phi]$, starting with any $\ar_0 \in \gleadstoinv(\phi)$. Observe that $\ar_0 \in \gargs[i, \phi]$. Given $k \in 2\N$, if $\ar_k \nileadstosti \phi$, define $\ar_{k + 2}$ using the deduction following the last lemma, obtaining $\ar_{k + 2} \in \gargs[i, \phi] \cap \dfp^\frac{k + 2}{2}(\ar_0)$. 
	By definition of an empirical theory, $\exists k \in \N \suchthat \dfp^k(\ar_0) = \emptyset$, thus, this process ends with some $\ar$ such that $\ar \ileadstosti \phi$.
\end{proof}

\subsection{Effectively comparing models}
Model: for a given $i$. Defends $\prop$. $\exists \ar_1 \in \args_\eta \suchthat \ar_1 \ileadstoi \prop$. Then, $\forall \ar_2 \in \gargs \suchthat (\ar_2, \ar_1) \ileadstoi ¬\prop: \exists \ar_3 \in \args_\eta \suchthat (\ar_3, \ar_2) \ileadstoi \prop.$

\section{Decision situation}
\NewDocumentCommand \ileadsto { o }{%
	\IfValueTF{#1}{%
		⇝^{#1}%
	}{%
		⇝%
	}%
}
\NewDocumentCommand \nileadsto { o }{%
	\IfValueTF{#1}{%
		\not⇝^{#1}%
	}{%
		\not⇝%
	}%
}
\NewDocumentCommand{\ileadstost}{O{}}{⇝^{#1}_\forall}
\NewDocumentCommand{\ileadstosts}{}{⇝_*}
\NewDocumentCommand{\ileadstos}{}{\overset{s}{⇝_i}}
\NewDocumentCommand{\ileadstostw}{O{}}{⇝^\mathit{w}_\forall}
\NewDocumentCommand{\ileadstostp}{O{}}{⇝^\mathit{pos}_\forall}
\NewDocumentCommand{\nileadstosts}{}{\not⇝_*}
\NewDocumentCommand{\Ti}{}{T_i}
\NewDocumentCommand{\nileadstost}{O{}}{\not⇝^{#1}_\forall}
\NewDocumentCommand{\ileadstoe}{O{}}{⇝^{#1}_\exists}
\NewDocumentCommand{\nileadstoe}{O{}}{\not⇝^{#1}_\exists}
\NewDocumentCommand{\ibeatse}{O{}}{⊳^{#1}_\exists}
\NewDocumentCommand \ibeatseinv { o }{
	\IfValueTF{#1}{%
		{⊳_\exists^{#1}}^{-1}%
	}{%
		⊳_\exists^{-1}%
	}%
}
\NewDocumentCommand{\zar}{}{\mathbf{0}}%zero, or empty, argument
\NewDocumentCommand{\mPhi}{}{\Phi_\gamma}
\NewDocumentCommand{\argsd}{}{S^\mathit{d}}

@@

\subsection{Example model}
\begin{itemize}
	\item $\ar_0 = \text{“Veg bec of ethics and health”}$
	\item $\ar_1 = \text{“Ethics is not defined”}$
	\item $\ar_2 = \text{“It is since Aristotle at least”}$
	\item $\ar_1' = \text{“Health isn’t important”}$
	\item $\ar_2' = \text{“Ask my grandmother”}$
	\item $\ar_1 \gbeats \ar_0$, $\ar_1' \gbeats \ar_0$
	\item $\ar_2 \gbeats \ar_1$, $\ar_2' \gbeats \ar_1'$
	\item $\ar_0 + \ar_2 \gbeats \ar_1$
	\item $\ar_1' \gbeats \ar_0 + \ar_2$
	\item $\ar_0 + \ar_2' \gbeats \ar_1'$
	\item $\ar_1 \gbeats \ar_0 + \ar_2'$
	\item $\ar_0 + \ar_2 + \ar_2' \gbeats \ar_1$
	\item $\ar_0 + \ar_2 + \ar_2' \gbeats \ar_1'$
\end{itemize}
